### 2022-10-12 chapters/introduction.tex
update : introduction

    \item On the other hand \cref{chapter:porgramming_langauges} will present a different aspect of the impact of energy consumption. In this chapter, we will analyze the energy consumption of services, where the execution time is not bounded. To do so, we will present two study cases.
    multiple programming languages, microservices architecture, web servers, the impact of energy consumption within a timeless context  \note{I haven't this part yet }

@@

\subsection*{Posters}
\begin{itemize}
    \item \emph{PyRAPL\@: Make your python green again}
          % TODO : ask romain about the date and the name of the event 
\end{itemize}
\subsection*{Future Work}
\begin{itemize}
    \item Reducing the energy consumption of Python using non-intrusive techniques
    \item Empirical analysis on the energy consumption of different web frameworks
    \item The impact of programming languages on energy consumption of web services (a case study of RPC protocol)
    \item THow do ORMs affect how much energy is used? A case study of Django and Flask
\end{itemize}

>>>>

    \item In contrast, \cref{chapter:porgramming_langauges} will use the flexibility provided by the micro-services architecture~\cite{dmitry2014micro} to analyze each programming language's energy behavior in light of various web scenarios to optimize the energy use of web services. We will first examine the effects of the various programming languages when dealing with the Remote Procedure Call (RPC) Protocol. In this instance, we will use two scaling factors: the number of concurrent clients and the size of the requests. Then we will compare $261$ web frameworks, each implementing the same website using seven use cases. This analysis aims to look at how each technology uses energy in different kinds of web situations.

@@

% \subsection*{Posters}
% \begin{itemize}
%     \item \emph{PyRAPL\@: Make your python green again}
%           % TODO : ask romain about the date and the name of the event 
% \end{itemize}
\subsection*{Future Work}
\begin{itemize}
    \item Reducing the energy consumption of Python using non-intrusive techniques
    \item Empirical analysis on the energy consumption of different web frameworks
    \item The impact of programming languages on energy consumption of web services (a case study of RPC protocol)
    \item THow do ORMs affect how much energy is used? A case study of Django and Flask
\end{itemize}

### 2022-10-12 chapters/programming_languages/programming_languages.tex
update : introduction

However, once deployed, the applications developed with such web frameworks do not exhibit the same performance as reported by the \emph{Web Framework Benchmarks} peri odically published by the \textsc{TechEmpower} company~\footnote{\url{https://www.techempower.com/benchmarks}}.

@@

\section{Conclusion}
This chapter aims to extend the work of \citeauthor{pereira_energy_2017}~\cite{pereira_energy_2017} by studying the energy footprint on other aspects than micro-benchmarking.
The main focus of this chapter is the behavior of programming languages within the context of web applications.
To do so, we have covered two case studies.
The first experiment is the impact of programming languages when developing RPC services.
We used the official implementation of \textsc{gRPC} library to build $25$ frameworks using $17$ programming languages.
In the second experiment, we look at how web frameworks affect energy consumption by creating a basic web application and comparing its performance, latency, and energy usage using the most common web frameworks.
Overall we had $261$ implementation using $35$ and three different databases.
For each implementation, we considered $7$ representative scenarios.
Each scenario is tested with several stress levels to study the scalability of the web frameworks.
Therefore, the final results cover $8,750$ use cases.

>>>>

However, once deployed, the applications developed with such web frameworks do not exhibit the same performance as reported by the \emph{Web Framework Benchmarks} periodically published by the \textsc{TechEmpower} company~\footnote{\url{https://www.techempower.com/benchmarks}}.

@@

\section{Conclusion}
This chapter aims to extend the work of \citeauthor{pereira_energy_2017}~\cite{pereira_energy_2017} by studying the energy footprint on other aspects than micro-benchmarking.
The main focus of this chapter is the behavior of programming languages within the context of web applications.
To do so, we have covered two case studies.
The first experiment is the impact of programming languages when developing RPC services.
We used the official implementation of \textsc{gRPC} library to build $25$ frameworks using $17$ programming languages.
In the second experiment, we look at how web frameworks affect energy consumption by creating a basic web application and comparing its performance, latency, and energy usage using the most common web frameworks.
Overall we had $261$ implementation using $35$ distinct programming languages and three different databases.
For each implementation, we considered $7$ representative scenarios.
Each scenario is tested with several stress levels to study the scalability of the web frameworks.
Therefore, the final results cover $8,750$ use cases.
